BIP Architectures and Open pNets

### 2019-02-01 2016-Weak-FH-Bisim/WeakBisim.tex
correction

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0\ldots m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           (\set{\beta^3_p}),\Pred\,^3_p, \Post_p^3   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
\Pred=\bigwedge_{i=0}^{m_1}\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\Pred_i^3\big(\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}(\subst{\Post^2}  \bigotimes_{j=0}^{i-1}\subst{\Post^3_i})\big)\\
\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\big(\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\big)
$\\

@@

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
$s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},\quad
\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  (\beta^1_{ij}) \dotcup  (\set{\beta^2}_i) \dotcup \mybigdotcup_{i=0}^{m_2} (\beta^3_{ij})
\\
\Pred\,'=\bigwedge_{i=0}^{m_1}
({\Pred_i^1}'\bigotimes_{i=0}^{i-1}\subst{{\Post_i^1}'})
\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land (\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'(\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'})\subst{{\Post^2}'}(\bigotimes_{j=0}^{i-1}\subst{{\Post^3_j}'}))\\
\Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}
$

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences, where sequence  $k$ has length $n_k$,  as follows:\\
$\forall p \in [0\ldots (n'-1)] Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
				{{\Post^1_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^2}''},  
				{{\Post^2}''}}
				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha_k}
				\ostate{v_{(n'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n'+1)\ldots (n_k-1)]\,\, Q\models{\openrule
			{
				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
				{{\Post^3_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
$\forall j \in {j\in (J\cap\Holes(Q))},\,
\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
\\
\Pred_k=\big(\!\!\!\bigwedge_{i=0}^{(n'-1)}\!\!
{\Pred_i^1}''\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^1}''}\big)
\land{\Pred^2}''\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^1}''}\land\\
\mbox{~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\Big(\!\!\!\bigwedge_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Pred^3_i}''\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\subst{{\Post^2}''}\Big)\bigotimes_{j=0}^{(i-1)}\subst{{\Post^3_j}''}\\
\Post_k=\Big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(n_k-1)}{\Post^3_i}''\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\Big)
$\\

@@

From cases 1, 2 and 3 we have for all $k\in [0\ldots n]$, $\beta_{kj_0}=\alpha_k$. Moreover, we have: $\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\

>>>>

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0\ldots m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           (\set{\beta^3_p}),\Pred\,^3_p, \Post_p^3   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
\Pred=\bigwedge_{i=0}^{m_1}\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\Pred_i^3\big((\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1})\big)\\
\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\big(\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}\big)
$\\

@@

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
$s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},
\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{ij}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{ij}}
\\
\Pred\,'=\bigwedge_{i=0}^{m_1}
({\Pred_i^1}'\bigotimes_{j=0}^{i-1}\subst{{\Post_j^1}'})
\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land 
(\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'(\bigotimes_{j=0}^{i-1}\subst{{\Post^3_j}'})\subst{{\Post^2}'}(\bigotimes_{j=0}^{m_1}\subst{{\Post^1_j}'}))\\
\Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{j=0}^{m_1}\subst{{\Post^1_j}'}
$

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
$\forall p \in [0\ldots (n'-1)] Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
				{{\Post^1_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^2}''},  
				{{\Post^2}''}}
				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha_k}
				\ostate{v_{(n'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n'+1)\ldots (n_k-1)]\,\, Q\models{\openrule
			{
				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
				{{\Post^3_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma'_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
$\forall j \in  (J\cap\Holes(Q)),\,
\displaystyle{\gamma'_{kj} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
\\
\Pred_k=\big(\!\!\!\bigwedge_{i=0}^{(n'-1)}\!\!
{\Pred_i^1}''\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^1}''}\big)
\land{\Pred^2}''\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^1}''}\land\\
~\qquad\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Pred^3_i}''\bigotimes_{j=n'+1}^{(i-1)}\subst{{\Post^3_j}''}\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\Big)\\
\Post_k=\Big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(n_k-1)}{\Post^3_i}''\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\Big)
$\\

@@

From cases 1, 2 and 3 we have for all $k\in [0\ldots n]$, $\beta_{kj_0}=\alpha_k$. Moreover, we have:\\ 
$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}=(\alpha'_k)^{k\in 1..n}=\{\alpha_p|p\in [0..m_1+m_2+1] \land \alpha_p\neq \tau\}$
%$\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\

### 2019-02-01 2018-Arch-pNets/arch-pNets.tex

\begin{example}[An open-transition]
  \label{Example:TimerOT3}
  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has \replaceSB{2 controllers 
  and 2 holes. O}{two coordinators and four dangling ports, which can be grouped into two holes (see \secn{encoding} below).  Disregarding the maximal progress priority, o}ne of its possible open-transitions is:\\[-2ex] \noteLH{maximal progress undefined}
%%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e. actions that are the result of a synchronisation and that we declare as \emph{non-observable}. Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector. This allows us to define a weak bisimilarity equivalence with p=compositional properties.}
%%   : 
%% \noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}
% \smallskip
%$  OT_1  = \openrule
%{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
%{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
%$
%\medskip
\begin{small}\[ \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z'= (z \cap (b1?zone;TopInt)+t) {\color{blue}\land (t' = t) \land (zone' = zone)},\\
    \{z:=z', {\color{blue}t := t'+1, zone := zone'}\} }
  {\ostate{11} \OTarrow{\alpha_0} \ostate{12}}
  \]
\end{small}\vspace{-1.5ex}
%
%The first one, $OT_1$, corresponds to the simultaneous initialisation
%of both controlers. No hole is active at that time, and the resulting
%global action is denoted $\alpha_4$.

It corresponds to the firing of the \replaceSB{connector
$''tick, fail, fail''$}{interaction $\listset{\NameTimer.\PortTick, \PortFail, \NameCtrl.\PortFail}$}. It states that, if the hole $B$ performs an action $fail$, and the (complex) guard is satisfied, then the variable $z$ is set to $z1$ (as specified by the guard), then the transition below the dotted line occurs and a global action labelled $\alpha_0$ occurs. Only the second pLTS performs a transition from state $1$ to state $2$.
The guard corresponds both to the guard of this transition and to synchronisation vector constraints.

>>>>

\begin{example}[An open-transition]
  \label{Example:TimerOT3}
We now briefly illustrate an open transition:
\begin{small}\[ \openrule
  {\{B\mapsto fail(b)\},
    t<Max \land b=true ,
    \{t' := t+1\} }
  {\ostate{11} \OTarrow{\alpha(t)} \ostate{12}}\vspace{-1.3ex}
  \]
\end{small}
%The first one, $OT_1$, corresponds to the simultaneous initialisation
%of both controlers. No hole is active at that time, and the resulting
%global action is denoted $\alpha_4$.
It requires the hole at label $B$ to fire a $fail(b)$ action, with the condition $b=true$ and the state variable $t<Max$. In this case, the global pNet goes from state $\ostate{11}$ to state $\ostate{12}$ where $t'=t+1$. This emits a global action $\alpha(t)$.
%It corresponds to the firing of the \replaceSB{connector
%$''tick, fail, fail''$}{interaction $\listset{\NameTimer.\PortTick, \PortFail, \NameCtrl.\PortFail}$}. It states that, if the hole $B$ performs an action $fail$, and the (complex) guard is satisfied, then the variable $z$ is set to $z1$ (as specified by the guard), then the transition below the dotted line occurs and a global action labelled $\alpha_0$ occurs. Only the second pLTS performs a transition from state $1$ to state $2$.
%The guard corresponds both to the guard of this transition and to synchronisation vector constraints.
